Kronos \& Krios: Evidence for accretion of a massive, rocky planetary system in a comoving pair of solar-type stars

### 2017-09-10 paper/ms.tex
intro

\newcommand{\todo}[1]{{\color{blue}TODO: #1\\}}
\newcommand*{\askjmb}[1]{{\bf #1}}

@@

Wide binary stars are valuable tools for studying star and planet formation as
well as Galactic dynamics and chemical evolution.
In the context of studying the evolution of the Milky Way, they are useful for
two main reasons.
First, because wide binaries are weakly bound systems that may be tidally
disrupted by, e.g., field stars, molecular clouds, or the Galactic tidal field,
their statistics can be informative of the Galactic mass distribution.
For example, the separation distribution of halo binaries has been used to
constrain the mass of massive compact halo objects
(\citealt{Yoo:2004aa,Quinn:2009,Allen:2014}).
They can also be used to test the ``chemical tagging'' hypothesis that stars
from the same birthplace may be traced back using detailed chemical abundance
patterns as birth tags (\citealt{2002ARA&A..40..487F}).
While any multiple-star system including massive open clusters can be used to
test the hypothesis, wide binaries have the advantage of being extremely
abundant, rendering their statistics a meaningful indication of whether the
hypothesis works.

Binary stars that form from the same birth cloud start with nearly identical
composition.
A differential analysis of the chemical composition of binary stars can reveal
their history through the chemical signatures related to planet formation or
accretion regardless of the Galactic chemical evolution.
\askjmb{
For example, \citealt{Fischer:2005aa} showed that the higher metallicity in
stars hosting close-in giant planets compared to those without likely promotes
the formation of giant planets by increasing the availability of small particle
condensates that form planetesimals.
}
On the other hand, if host stars are polluted after their birth by rocky
planetary material with high refractory-to-volatile ratio, the convective
envelope of the stars may be enhanced in refractory elements (e.g., \elem{Fe})
compared to their initial state (e.g., \citealt{Pinsonneault:2001aa}).
Thus, differences in planet formation or accretion in two otherwise identical
stars may imprint differences in chemical abundances that depend on the
condensation temperature (\Tcondens).

High resolution spectroscopic studies of binary star systems hosting at least
one planet (\citealt{2011ApJ...740...76R,2014ApJ...790L..25T,Teske:2013aa,
  Mack:2014aa,Liu:2014aa,Teske:2015aa,Saffe:2015aa,
  Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab})
have yielded varied results:
while some systems appear to have undetectable differences
(see also \citealt{Desidera:2004aa,Gratton:2001aa}), other
studies have reported a \Tcondens-dependent difference in abundance
with higher-\Tcondens\ elements showing larger differences.
A possible explanation for the difference is that
forming more gas giants or rocky planets leads to
an overall or \Tcondens-dependent depletion
(\citealt{Ramirez:2015aa,Biazzo:2015aa}).
Alternatively, late time accretion of refractory-rich planetary material to the
relatively refractory-rich star can also produce the trend.
The observed differences are $\lesssim 0.1$~dex even in the most dramatic case,
and often at $\approx 0.05$~dex level making them challenging to detect even
with a careful analysis of high-resolution, high signal-to-noise ratio spectra,
and differential analyses of two stars that are very similar in their
stellar parameters.
We refer the readers to Appendix~\ref{app:review} for a review of
a handful of individual pairs studied in their detailed chemical abundances
(see also \citealt{2016arXiv161104064M}).

>>>>

\newcommand{\todo}[1]{{\color{blue}TODO: #1\\}}
\newcommand{\apw}[1]{{\color{purple}APW asks: #1}}
\newcommand*{\askjmb}[1]{{\bf #1}}

@@

Wide binary stars are valuable tools for studying star and planet formation as
well as Galactic dynamics and chemical evolution.
In the context of studying the evolution of the Milky Way, they are useful for
two main reasons.
First, because wide binaries are weakly bound systems that may be tidally
disrupted by, e.g., field stars, molecular clouds, or the Galactic tidal field,
their statistics can be informative of the Galactic mass distribution.
For example, the separation distribution of halo binaries has been used to
constrain the mass of massive compact halo objects
(\citealt{Yoo:2004aa,Quinn:2009,Allen:2014}).
They can also be used to test the ``chemical tagging'' hypothesis that stars
from the same birthplace may be traced back using detailed chemical abundance
patterns as birth tags (\citealt{2002ARA&A..40..487F}).
While any multiple-star system, including massive open clusters, can be used to
test the hypothesis, wide binaries have the advantage of being extremely
abundant, rendering their statistics a meaningful indication of whether the
hypothesis works.

Binary stars that form from the same birth cloud start with nearly identical
composition.
A differential analysis of the chemical composition of binary stars can reveal
their history through the chemical signatures related to planet formation or
accretion regardless of Galactic chemical evolution.
\askjmb{
For example, \citealt{Fischer:2005aa} showed that higher metallicity
stars more likely host close-in giant planets, which likely promotes
the formation of giant planets by increasing the availability of small particle
condensates that form planetesimals.
}
On the other hand, if host stars are polluted after their birth by rocky
planetary material with high refractory-to-volatile ratio, the convective
envelope of the stars may be enhanced in refractory elements (e.g., \elem{Fe})
compared to their initial state (e.g., \citealt{Pinsonneault:2001aa}).
Thus, differences in planet formation or accretion in two otherwise identical
stars may imprint differences in chemical abundances that depend on the
condensation temperature (\Tcondens).

High resolution spectroscopic studies of binary star systems hosting at least
one planet (\citealt{2011ApJ...740...76R,2014ApJ...790L..25T,Teske:2013aa,
  Mack:2014aa,Liu:2014aa,Teske:2015aa,Saffe:2015aa,
  Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab})
have yielded varied results:
while some systems appear to have undetectable differences
(see also \citealt{Desidera:2004aa,Gratton:2001aa}), other
studies have reported a \Tcondens-dependent difference in abundance
with higher-\Tcondens\ elements showing larger differences.
A possible explanation for the difference is that
forming more gas giants or rocky planets leads to
an overall or \Tcondens-dependent depletion of higher-\Tcondens\ elements that
eventually accrete onto the host star
(\citealt{Ramirez:2015aa,Biazzo:2015aa}).
Alternatively, late time accretion of refractory-rich planetary material to the
relatively refractory-rich star can also produce the trend \apw{do you mean "relatively refractory-poor star" instead?}.
The observed differences are $\lesssim 0.1$~dex even in the most dramatic case,
and often closer to $\approx 0.05$~dex, making them challenging to detect even
with a careful analysis of high-resolution, high signal-to-noise ratio spectra,
and differential analyses of two stars that are very similar in their
stellar parameters.
We refer the readers to Appendix~\ref{app:review} for a review of
a handful of individual pairs studied in their detailed chemical abundances
(see also \citealt{2016arXiv161104064M}).
